Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor/draft] vectorial -> vector, tensorial -> tensor
add Stephan's new address, modify title

\title{Constraining tensorial and scalar couplings with
  $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
}

@@

\author{Stephan Jahn}
\affiliation{
  \todo{neue Adresse}
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
  nonstandard tensorial and scalar contributions are enhanced with respect
  to vectorial ones. We use latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent
  constraints on tensorial and scalar effective couplings and determine their
  impact on not yet measured angular observables in
  $B\to K^*\bar\mu\mu$, which feature the same suppression of vectorial couplings.
  Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings.
\end{abstract}

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
branching fraction of $B_s\to \bar\mu\mu$ and the
treatment of theory uncertainties are relegated to appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$)
operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence
of the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background\footnote{The leading
QED corrections to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
corresponding effects in $B\to K \bar\ell\ell$.}.

This picture does not change in the presence of new physics contributions to
vectorial and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
non-vanishing tensorial or scalar contributions are enhanced unless the
dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensorial couplings whereas $A_{\rm FB}^\ell$ to
the interference of tensorial and scalar couplings.

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensorial coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available. 
      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$ 
            or even $\in [-0.5, +0.5]$?}}
  \label{fig:FHvsCT}
\end{figure*}

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial ones
present in the SM or their respective interference terms. These are $J_{6c}$
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
with explicit formulas given in \refapp{app:BKstarellell}.
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensorial and scalar operators,
  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensorial contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensorial contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensorial and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only
constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
\refeq{eq:AFB-dependence} are measured in the angular distribution \refeq{eq:ang-distr}
of $B\to K \bar\ell\ell$ being normalised to the decay width $\Gamma_\ell$, such
that uncertainties due to form factors can cancel in part \cite{Bobeth:2007dw,
Bobeth:2012vn}. On the other hand, $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$ appear in the unnormalised angular distribution of
$B\to K^* \bar\ell\ell$ and so-called ``optimised'' versions $S_1$, $M_1$ and
$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw},
respectively, where form factors cancel in the limit of $m_b \to \infty$.
For the high-$q^2$ region potential normalisations are discussed in
\refapp{app:BKstarellell}, which could serve to form optimised observables for
special scenarios of either vanishing chirality-flipped vectorial or tensorial
or scalar couplings. In the most general case, however, there are no optimised
observables at high-$q^2$. Although form factors do not cancel in this case, it
might be still advantageous to use normalisations, for example when the overall
normalisation of $B\to K^*$ form factors constitutes a major theoretical
uncertainty.

@@

To illustrate the sensitivity of $F_H^\ell$ to tensorial couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
the sensitivity to tensorial couplings is highest for $F_H^\ell$ at high $q^2$,
also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensorial couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of
tensorial couplings. Moreover, the dependence on vectorial couplings is such that
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

@@

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio, the lepton forward-backward
asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
additional constraints on the real and imaginary parts of vectorial couplings.

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensorial couplings \label{sec:tensor}}

>>>>

\title{Constraints on tensor and scalar couplings from
  $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
}

@@

\author{Stephan Jahn}
\affiliation{
  Max Planck institute for physics, Munich.\\
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
  nonstandard tensor and scalar contributions are enhanced with respect
  to vector ones. We use latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent
  constraints on tensor and scalar effective couplings and determine their
  impact on not yet measured angular observables in
  $B\to K^*\bar\mu\mu$, which feature the same suppression of vector couplings.
  Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings.
\end{abstract}

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensor and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vector couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensor couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensor and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensor and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensor and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
branching fraction of $B_s\to \bar\mu\mu$ and the
treatment of theory uncertainties are relegated to appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
chiral structure. There are dipole ($i = 7,7')$ and vector ($i = 9,9',10,10'$)
operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence
of the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background\footnote{The leading
QED corrections to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
corresponding effects in $B\to K \bar\ell\ell$.}.

This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
non-vanishing tensor or scalar contributions are enhanced unless the
dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings whereas $A_{\rm FB}^\ell$ to
the interference of tensor and scalar couplings.

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$
            or even $\in [-0.5, +0.5]$?}}
  \label{fig:FHvsCT}
\end{figure*}

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensor and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones
present in the SM or their respective interference terms. These are $J_{6c}$
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
with explicit formulas given in \refapp{app:BKstarellell}.
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensor and scalar operators,
  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensor and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
\refeq{eq:AFB-dependence} are measured in the angular distribution \refeq{eq:ang-distr}
of $B\to K \bar\ell\ell$ being normalised to the decay width $\Gamma_\ell$, such
that uncertainties due to form factors can cancel in part \cite{Bobeth:2007dw,
Bobeth:2012vn}. On the other hand, $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$ appear in the unnormalised angular distribution of
$B\to K^* \bar\ell\ell$ and so-called ``optimised'' versions $S_1$, $M_1$ and
$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw},
respectively, where form factors cancel in the limit of $m_b \to \infty$.
For the high-$q^2$ region potential normalisations are discussed in
\refapp{app:BKstarellell}, which could serve to form optimised observables for
special scenarios of either vanishing chirality-flipped vector or tensor
or scalar couplings. In the most general case, however, there are no optimised
observables at high-$q^2$. Although form factors do not cancel in this case, it
might be still advantageous to use normalisations, for example when the overall
normalisation of $B\to K^*$ form factors constitutes a major theoretical
uncertainty.

@@

To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
the sensitivity to tensor couplings is highest for $F_H^\ell$ at high $q^2$,
also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensor couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of
tensor couplings. Moreover, the dependence on vector couplings is such that
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

@@

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vector couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio, the lepton forward-backward
asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
additional constraints on the real and imaginary parts of vector couplings.

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensor couplings \label{sec:tensor}}
